Software Ticket Quality

### 2017-10-30 proposal/mprop.tex
Add paper on evaluating IT quality in e-gov

>>>>

\textbf{Evaluating IT Quality in E-Government 
        Environment}\cite{prybutok2008evaluating}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to identify if leadership and IT quality
    can lead to positive outcomes in an e-government environment.
  \item \textbf{What was the method?}
    They conducted a web survey to gather data and test their hypotheses. They
    assessed the City of Denton's e-government initiatives, including current 
    plans and implementations.
  \item \textbf{What did they learn?}
    They learned that the MBNQA leadership triad (leadership, strategic
    planning and customer/market focus) had a positive impact on the IT quality
    triad (information, system and service quality). Moreover, they found out
    that both leadership and IT quality improved the benefits.
  \item \textbf{Relevance to our work}: even though the environment presented
    in the paper was an e-government, it is useful to see how the organization 
    around a project as well as IT quality can lead to a better functioning of the 
    system. Thus, in our research, it can prove helpful in choosing the right 
    open source project to gather and analyse the data from.
\end{itemize}
